---
title: "Data engineering assignment"
subtitle: 'MongoDB dataset report'
author: "Kory"
output: word_document
date: "2024-03-24"
---

```{r setup, include=FALSE, echo=FALSE}
source(file=paste(getwd(),"/mongodb_dataset_main", sep="")) 
```

# Mongo DB dataset
## Looking at the entire dataset
```{r report_export_01, include=TRUE, echo=FALSE}
paste("number of missing values in entire dataset: ", export_01_0001, sep = "")
```
There are no missing values in this dataset


```{r report_export_02, include=TRUE, echo=FALSE}
export_02_0001
export_02_0002

paste("the range of scores (difference between the min and max scores): ", diff(export_02_0003), sep = "")


```

There are 400,000 rows and 4 columns in total

  * There are 10,000 students with a unique student ID 
  * There are 501 classes with a unique class ID 
  * There are 3 assignment types, which is as we'd expect
  * There are 400,000 unique scores, which is unexpected but makes sense as there are at least 7 decimal places in the scores, which range from ~ 0 to ~ 100. There'd be less unique scores if the score values were integers

```{r report_export_03, include=TRUE, echo=FALSE}
paste("mean: ", export_03_0001, sep = "")
paste("median: ", export_03_0002, sep = "")
paste("maximum: ", export_03_0003, sep = "")
paste("minimum: ", export_03_0004, sep = "")
paste("1st quartile: ", export_03_0005, sep = "")
paste("3rd quartile: ", export_03_0006, sep = "")
paste("standard deviation: ", export_03_0007, sep = "")
```

For all the scores in the dataset, we can derive the mean, median, minimum, maximum, 1st quartile, 3rd quartile, and standard deviation values


```{r report_export_04, include=TRUE, echo=FALSE}
export_04_0001
```


We can also show the distribution of scores for all of the assignments (quiz, exam, homework) that students have ever done

## Looking at subsets of the dataset


```{r report_export_05, include=TRUE, echo=FALSE}
export_05_0001
```

We can look up a student (e.g. the student with a 'student_id' of 1) and see how well that student has done compared to other students enrolled in the same classes. 

  * To calculate the score each student achieved in each of their classes, an average of all of their scores for all of the assessment items in that class was used.
  * To calculate the class average for each class, an average of all of the average scores a student received for each class was used
  * To calculate quartile 1 and 3 values, I obtained the value at the 25% and 75% percentile for all of the average scores a student received for each class


